Appendix: Quantitative, Multispecies Monitoring at a Continental Scale

### 2025-02-27 Appendix_plain_v1.tex
Updates from Overleaf

We constructed mock communities with even and skewed species total genomic DNA using Qubit HS assay quantification method. We then quantified the concentration of the 12S rRNA gene using MarVer1 primers (forward: CGTGCCAGCCACCGCG; reverse: GGGTATCTAATCCYAGTTTG \cite{valsecchi2020}), which perfectly matched the template to give unbiased estimates of concentration, using ddPCR (Bio-Rad, Inc., QX200 Droplet Digital PCR system). Each tissue of each species was quantified in a 22 $\mu$L reaction consisted of 2 $\mu$L of DNA template from genomic DNA , 11 $\mu$L of ddPCR EvaGreen (Bio-Rad), 0.22 $\mu$L of each forward and reverse primers (10 uM), and 0.56 $\mu$L of nuclease free water (see SI Appendix Table S.\ref{tab:mock_table} for DNA quantification results). The thermocycler reactions were run in C1000 Touch Thermal Cycler with 96-Deep Well Reaction Module (Bio-Rad) using the PCR program as follows: 2 min at 50°C for enzyme activation, 2 min at 95°C for initial denaturation, and 40 cycles of denaturation for 1 sec at 95°C and primer annealing and elongation for 30 sec min at 60°C, with a ramp rate of 2°C per s and heldat 4°C until droplets were read. Droplets were determined to be positive after drawing a threshold based on NTCs.

@@

We developed a joint model for modeling DNA concentration in the coastal ocean using single-species qPCR data Pacific hake and metabarcoding data from the 12S MiFish Universal primer. This work builds off previous single-species eDNA models constructed for Pacific hake \cite{shelton2022} and models for joining qPCR and metabarcoding data \cite{guri2024a}. Here qPCR observations provide information about DNA concentration for one species (Pacific hake) and the metabarcoding data provide information about species composition within a sample (i.e. proportions that sum to one).  In combination, these two data sources allow for estimation of DNA concentrations for all species observed by metabarcoding.

@@

We developed a state-space framework for modeling hake DNA concentration in the coastal ocean building and modifying the work of \cite{shelton2022}.  State-space models separate the true biological process from the methods used to observe the process. Let $D_H(x,y,d)$ be the true, but unobserved concentration of hake DNA (log DNA $copies$ $\mu L^{-1}$) present at spatial coordinates $\{x,y\}$ (eastings and northings, respectively, in km) and sample depth $d$ (meters). Hereafter we refer to a combination of spatial location and depth as a ``station". Let $\psi$ be the intercept representing the mean hake DNA concentration and $\epsilon(x,y,d)$ be a random effect that allows for the effect of spatial location and water depth. We write these as additive on the log-scale,

\begin{align}
  D_H(x,y,d) &= \psi + \epsilon(x,y,d) \\
  \epsilon(x,y,d) &\sim N(0,\sigma_D)
\end{align}

@@

Unfortunately, qPCR does not directly measure DNA concentration. Instead qPCR measures the PCR cycle at which a 2$\mu L$ aliquot of a extacted DNA was detected to fluoresce and compares that observation against the flourescence pattern of samples of known DNA concentration ("the standard curve"). This provides an estimate of DNA concentration for each unknown sample. Each water sample is analyzed using at least 3 independent qPCR replicates to account for laboratory and machine variability. In addition to qPCR variability among replicates, we also have to account for modifications that affect each water sample and occurred during water sampling and processing. First, we have three offsets that modify the true DNA concentration to affect what we observed in the qPCR. For water sample $i$: 1) $V_i$ is the proportion of 2.5 L filtered from Niskin $i$ (occasionally some seawater was spilled or not filtered; $V_i =1$ for the vast majority of samples); 2) $I_i$ is the known dilution used to on sample $i$ to eliminate PCR inhibition. PCR inhibition is most commonly observed in surface samples and is vanishingly rare for samples collected below 100m; 3) $\mathbf{I}\zeta$ is an estimated offset for an ethanol wash error ($\zeta$ is the estimated effect of the wash error and $\mathbf{I}$ is an indicator variable where $\mathbf{I}=1$ for affected samples and $\mathbf{I}=0$ otherwise; see \cite{shelton2022} Supp S1 for additional description). Here we fix $\zeta$ = -1.15 based on previous analyses \cite{shelton2022}.

@@

In addition to the qPCR observations, we used the MiFish primer and high throughput sequencing to detect and enumerate the sequences of other fish species in the same samples that were examined for hake DNA. Again, we are interested in determining the DNA concentration of each focal species in each sample. Unfortunately, metabarcoding data is compositional data \cite{gloor2017, shelton2023}, and so while it can inform the relative abundance of species within a sample, alone it cannot provide estimates of DNA concentration. Fortunately, the qPCR data from Pacific hake provides information about DNA concentration for one species and the metabarcoding data provides information about the relative abundance for tens of species, including hake. Here, we follow and extend the metabarcoding model developed by \cite{shelton2023} and show how it links with the qPCR model above.

As above, we let $D_s(x,y,d)$ be the log-scale eDNA concentration but now for species $s$. We let $E_{si}(x,y,d)$ be the log-DNA concentration for each species in each bottle. Importantly one of the $s$ species is Pacific hake and so connects to the qPCR model above. Metabarcoding reads are compositional and so we model the DNA concentration relative to one another using the additive log-ratio transformation (ALR; \textbf{Aitchison 1986}).  We define a reference species in each sample, $R$, with the species used as a reference varying among sample. Let $\alpha_s$ be the per PCR cycle log amplification rate for species $s$ (see \cite{shelton2023}).  We can then calculate $\nu_{si}$, the log-ratio between species $s$ and the reference species after accounting for amplification bias (see Mock Communities below),

@@

\begin{align} 
 \nu_{sm} &= \left( L_{sm} - L_{Rm}\right) + N_{PCR} \left(\alpha_s - \alpha_{Ri} \right) \\
  \pi_{sm} &= \dfrac{e^{\nu_{sm}}}{\sum_{s=1}^S e^{\nu_{sm}}} \\
  \boldsymbol{R}_{m} & \sim Multinomial\left(\boldsymbol{\pi}_{m},T_{m}\right) 
\end{align}

@@

\section*{Model convergance}
Convergence and reliability of the Bayesian model were assessed through comprehensive diagnostics. All parameters (SI Appendix Table S.\ref{tab:priortable}) exhibited Gelman-Rubin convergence statistics ($\hat{R} < 1.05$) and effective sample sizes (ESS) exceeding 200 per parameter, indicating successful convergence and efficient mixing of the six independent chains (SI Appendix Fig. S.\ref{tab:diagnostics}\textit{A}). An exception was the parameter $\psi$ (mean hake), which showed marginally lower mixing ESS$_\psi$ = 149.7) suggesting mild autocorrelation but no critical failure of convergence.

No divergent transitions were detected during sampling, and the maximum tree depth was not exceeded, indicating no issues with divergence or exploration limits (SI Appendix Fig. S.\ref{tab:diagnostics}\textit{B}). The posterior likelihood demonstrated convergence before the sampling phase began, with all chains exhibiting high mixing, confirming robust exploration of the parameter space (Fig. S.\ref{tab:diagnostics}\textit{B}).

Prior sensitivity analyses revealed that posterior estimates differed from priors, demonstrating that the posteriors were appropriately updated based on the observed data rather than being heavily influenced by prior assumptions (SI Appendix Fig. S.\ref{tab:prior_sensitivity}). Additionally, the posterior predictive checks (PPC) demonstrated that the model reliably reproduced the observed data, supporting the validity of parameter estimates (SI Appendix Fig. S.\ref{tab:PPC}).

Collectively, these diagnostics confirm the reliability and validity of the Bayesian model used here.

@@

\begin{figure*}[tbhp] 
\centering
\includegraphics[width=16cm]{plots/DAG-Ole.pdf} 
\caption{Schematic for the statistical models to produce species distributions. Three sets of observations (orange) were used simultaneously to provide estimates of eDNA concentration for  twelve fish species (blue) from which we derive smoothed predictions of DNA concentration (green). Mock communities for metabarcoding (yellow) were estimated externally and provided estimated $\alpha_s$ that were used in the joint model. Notation for parameters, subscripts, and observations are indicated in gray.}
\label{fig:DAG2}
\end{figure*}

%%% Each figure should be on its own page
%\begin{figure}
%\centering
%\includegraphics[width=0.89\textwidth]{plots/4_Figure_4.jpg}
%\caption{Vertical (A) and latitudinal (B) distribution of eDNA concentrations grouped in ecological groups (surface south, surface north, midwater, and deepwater). Mean eDNA concentration of vertical distribution is shown with dots and 99\% upper quantile with ticks (A). Probability density functions (PDF) of estimated eDNA concentrations across latitudinal gradients (B; square root transformed of x-axis to enhance low concentration peaks). Key geographic features, such as the Columbia River and Heceta Bank, are marked to indicate alignment of species distributions.}
%\end{figure}

@@

@@

%%% Each figure should be on its own page
\begin{figure}
\centering
\includegraphics[width=0.88\textwidth]{plots/11_Diagnostic_Fig_1.jpg}
\caption{Bayesian model diagnostic plots including $\hat{R}$ and ESS for each parameter (A) and posterior likelihood, acceptance rate, tree depth, divergence transition, and step size for each iteration in each chain (including warm up phase; B).}
\label{tab:diagnostics}
\end{figure}

%%% Each figure should be on its own page
\begin{figure}
\centering
\includegraphics[width=0.98\textwidth]{plots/12_Diagnostic_Fig_2.jpg}
\caption{Prior sensitivity plots indicating the distribution of priors in red and posteriors in black with dots indicating the mean and ticks showing 95\% credible interval.}
\label{tab:prior_sensitivity}
\end{figure}

%%% Each figure should be on its own page
\begin{figure}
\centering
\includegraphics[width=0.98\textwidth]{plots/9_Supplementary_Figure_5.jpg}
\caption{Mean posterior predictions for three model compartments, qPCR continuous model (A), qPCR occupancy model (B), mock community model (C and D on species proportions and number of reads) and metabarcoding model (E)}
\label{tab:PPC}
\end{figure}

\clearpage
\begin{table}\centering
\caption{Initial proportional abundances (measured by amplifying the 12S rRNA gene using MarVer1 primers \cite{valsecchi2020} and ddPCR QX200 Droplet Digital PCR system (Bio-Rad, Inc.)) of the selected species (n=12) across different mock communities (n=8). NA represent no DNA template included.}
    \begin{tabular}{lcccccccc}
        \toprule
        {Species} & \multicolumn{2}{c}{Mock1} & \multicolumn{2}{c}{Mock2} & \multicolumn{2}{c}{Mock3} & \multicolumn{2}{c}{Mock4} \\
        & Even & Skew & Even & Skew & Even & Skew & Even & Skew \\
        \midrule
        \textit{Clupea pallasii}           & 0.437 & 0.325  & 0.042  & 0.009     & -         & -          & 0.025      & 0.038 \\
        \textit{Engraulis mordax}          & 0.122 & 0.034  & 0.15 & 0.15       & 0.146      & 0.16       & 0.308      & 0.478 \\
        \textit{Leuroglossus stilbius}     & 0.108 & 0.29   & - & -         & -         & -         & -         & - \\    
        \textit{Merluccius productus}      & 0.079 & 0.144  & 0.12 & 0.06       & 0.117      & 0.075      & 0.247      & 0.287 \\
        \textit{Microstomus pacificus}     & -    & -     & 0.057  & 0.215     & -         & -         & -         & - \\    
        \textit{Sardinops sagax}           & 0.028 & 0.033  & 0.14 & 0.035      & 0.137      & 0.025      & 0.289      & 0.131 \\
        \textit{Scomber japonicus}         & -    & -     & 0.122  & 0.053      & 0.119      & 0.027     & -         & - \\    
        \textit{Sebastes entomelas}        & -    & -     & - & -          & 0.068      & 0.218     & -         & - \\    
        \textit{Stenobrachius leucopsarus} & -    & -     & - & -          & 0.356      & 0.487     & -         & - \\    
        \textit{Tactostoma macropus}       & -    & -     & 0.13 & 0.324     & -         & -         & -         & - \\    
        \textit{Tarletonbeania crenularis} & -    & -     & 0.083  & 0.124     & -         & -         & -         & - \\    
        \textit{Thaleichthys pacificus}    & 0.123 & 0.113  & 0.099  & 0.012     & -         & -          & 0.013      & 0.021 \\
        \textit{Trachurus symmetricus}     & 0.103 & 0.06   & 0.057  & 0.018      & 0.056      & 0.008      & 0.118      & 0.04 \\
        \bottomrule
    \end{tabular}
    \label{tab:mock_table}
\end{table}
\clearpage

\begin{table}[h]
    \centering
    \begin{tabular}{lll}
         & \textbf{Description} & \textbf{Prior} \\
&Data & \\
\hline
$K$ & known DNA concentration from qPCR stsandards in ln(copies/$\mu$L) & - \\
$Z$ & qPCR amplification (yes=1; no=0) & - \\
$Y$ & qPCR cycle threshold (Ct) & - \\
$R$ & metabarcoding number of reads & - \\
$T$ & total number of reads for all S species & - \\
$N_{PCR}$ & number of metabarcoding PCR cycles & - \\
$L$ & known DNA concentration from mock commuinties in ln(copies/$\mu$L) & - \\
$V$ & volume filtered and aliquote dilution offset & -\\
$I$ & aliquote dilution factor & -\\

&&\\
&State processes&\\
\hline
$E_{s\neq H}$ & unknown DNA concentration in ln(copies/$\mu$L) & $\mathcal{N}(0,5)$\\
$D$ & unknown DNA concentration in ln(copies/$\mu$L)& - \\
$F$ & smoothed DNA concentration in copies/L & - \\
&&\\

&Parameters&\\
\hline
$\psi$& overall mean hake eDNA concentration in ln(copies/$\mu$L) & $\mathcal{N}(2,2)$\\
$\epsilon_{j}$& spatial and depth specific random effect & $\mathcal{N}(0,\tau)$\\
$\tau$& standard deviation of biological replicate random effect & $\mathcal{TN}(0,0.2;0, +\infty)$\\

$\delta$& biological replicate random effect & $\mathcal{N}(0,\sigma_D)$\\
$\sigma_D $& standard deviation of spatial and depth specific random effect & $\mathcal{TN}(0,3;0, +\infty)$\\

$\phi$& intercept of the qPCR probability of detection relationship & $\mathcal{N}(3,1)$\\
$\beta_0$& intercept of the linear relation between the mean Ct values&$\mathcal{N}(39,3)$\\
&and eDNA concentration (K and E) & \\
$\beta_1$& slope of the linear relation between the mean Ct values and &$\mathcal{N}(-1.4,0.05)$\\
&eDNA concentration (K and E) & \\
$\gamma_0$& intercept of the linear relation between the standard deviation&$\mathcal{N}(0,1)$\\
&of Ct values and eDNA concentration (K and E) & \\
$\gamma_1$& intercept of the linear relation between the standard deviation &$\mathcal{N}(0,1)$\\
&of Ct values and eDNA concentration (K and E) & \\
$\alpha_s$& species amplification efficiency relative to reference species (R) & fixed (SI Appendix Table S.\ref{tab:alphas})\\
$\zeta$& ethanol wash effect & fixed (-1.15)\\
&&\\
&Index&\\
\hline
$s$& species ($H$ = Hake) & -\\
$j$& location (northing(x), easting(y), depth(d)))& -\\
$i$& biological replicate & -\\
$r$& technical replicate & -\\
$p$& qPCR plate & -\\
$m$& mock community sample & -\\
$q$& qPCR standard aliquote sample & -\\
$R$& metabarcoding reference species & -\\

    \end{tabular}
    \caption{Data, state processes, parameters, and subscripts employed in the joint Bayesian model and their prior distributions}
    \label{tab:priortable}
\end{table}

\clearpage
\begin{table}\centering
\caption{Species specific metabarcoding amplification efficiency relative to reference species (R; \textit{Merluccius productus} here).}
    \begin{tabular}{lc}
\textbf{Species} & $\alpha$ \\
\textit{Clupea pallasii} &   -0.00138 \\
\textit{Engraulis mordax} &    0.00557 \\
\textit{Leuroglossus stilbius} &   -0.00390 \\
\textit{Microstomus pacificus} &    0.00194 \\
\textit{Sardinops sagax} &    0.00705 \\
\textit{Scomber japonicus} &    0.00434 \\
\textit{Sebastes entomelas} &    0.00459 \\
\textit{Stenobrachius leucopsarus} &    0.00970 \\
\textit{Tactostoma macropus} &   -0.00091 \\
\textit{Tarletonbeania crenularis} &    0.00144 \\
\textit{Thaleichthys pacificus} &   -0.00506 \\
\textit{Trachurus symmetricus} &   -0.00875 \\
\textit{Merluccius productus} &    0.00000 \\
    \end{tabular}
        \label{tab:alphas}
\end{table}
\clearpage

\bibliography{clean_bib.bib}
\end{document}

>>>>

We constructed mock communities with even and skewed species total genomic DNA using Qubit HS assay quantification method. We then quantified the concentration of the 12S rRNA gene using MarVer1 primers (forward: CGTGCCAGCCACCGCG; reverse: GGGTATCTAATCCYAGTTTG \cite{valsecchi2020}), which perfectly matched the template to give unbiased estimates of concentration, using ddPCR (Bio-Rad, Inc., QX200 Droplet Digital PCR system). Each tissue of each species was quantified in a 22 $\mu$L reaction consisted of 2 $\mu$L of DNA template from genomic DNA , 11 $\mu$L of ddPCR EvaGreen (Bio-Rad), 0.22 $\mu$L of each forward and reverse primers (10 uM), and 0.56 $\mu$L of nuclease free water. The thermocycler reactions were run in C1000 Touch Thermal Cycler with 96-Deep Well Reaction Module (Bio-Rad) using the PCR program as follows: 2 min at 50°C for enzyme activation, 2 min at 95°C for initial denaturation, and 40 cycles of denaturation for 1 sec at 95°C and primer annealing and elongation for 30 sec min at 60°C, with a ramp rate of 2°C per s and heldat 4°C until droplets were read. Droplets were determined to be positive after drawing a threshold based on NTCs.

@@

We developed a joint model for modeling DNA concentration in the coastal ocean using single-species qPCR data Pacific hake and metabarcoding data from the 12S MiFish Universal primer. This work builds off previous single-species eDNA models constructed for Pacific hake (Shelton et al. 2022) and models for joining qPCR and metabarcoding data (Guri et al. 2024). Here qPCR observations provide information about DNA concentration for one species (Pacific hake) and the metabarcoding data provide information about species composition within a sample (i.e. proportions that sum to one).  In combination, these two data sources allow for estimation of DNA concentrations for all species observed by metabarcoding.

@@

We developed a state-space framework for modeling hake DNA concentration in the coastal ocean building and modifying the work of Shelton et al. (2022).  State-space models separate the true biological process from the methods used to observe the process. Let $D_H(x,y,d)$ be the true, but unobserved concentration of hake DNA (log DNA $copies$ $\mu L^{-1}$) present at spatial coordinates $\{x,y\}$ (eastings and northings, respectively, in km) and sample depth $d$ (meters). Hereafter we refer to a combination of spatial location and depth as a ``station". Let $\psi_0$ be the intercept representing the mean hake DNA concentration and $\epsilon(x,y,d)$ be a random effect that allows for the effect of spatial location and water depth. We write these as additive on the log-scale,

\begin{align}
  D_H(x,y,d) &= \psi_0 + \epsilon(x,y,d) \\
  \epsilon(x,y,d) &\sim N(0,\sigma_D)
\end{align}

@@

Unfortunately, qPCR does not directly measure DNA concentration. Instead qPCR measures the PCR cycle at which a 2$\mu L$ aliquot of a extacted DNA was detected to fluoresce and compares that observation against the flourescence pattern of samples of known DNA concentration ("the standard curve"). This provides an estimate of DNA concentration for each unknown sample. Each water sample is analyzed using at least 3 independent qPCR replicates to account for laboratory and machine variability. In addition to qPCR variability among replicates, we also have to account for modifications that affect each water sample and occurred during water sampling and processing. First, we have three offsets that modify the true DNA concentration to affect what we observed in the qPCR. For water sample $i$: 1) $V_i$ is the proportion of 2.5 L filtered from Niskin $i$ (occasionally some seawater was spilled or not filtered; $V_i =1$ for the vast majority of samples); 2) $I_i$ is the known dilution used to on sample $i$ to eliminate PCR inhibition. PCR inhibition is most commonly observed in surface samples and is vanishingly rare for samples collected below 100m; 3) $\mathbf{I}\zeta$ is an estimated offset for an ethanol wash error ($\zeta$ is the estimated effect of the wash error and $\mathbf{I}$ is an indicator variable where $\mathbf{I}=1$ for affected samples and $\mathbf{I}=0$ otherwise; see Shelton et al. 2022 Supp S1 for additional description). Here we fix $\zeta$ = XXX based on previous analyses (Shelton et al. 2022).

@@

In addition to the qPCR observations, we used the MiFish primer and high throughput sequencing to detect and enumerate the sequences of other fish species in the same samples that were examined for hake DNA. Again, we are interested in determining the DNA concentration of each focal species in each sample. Unfortunately, metabarcoding data is compositional data \cite{glor2017, shelton2023}, and so while it can inform the relative abundance of species within a sample, alone it cannot provide estimates of DNA concentration. Fortunately, the qPCR data from Pacific hake provides information about DNA concentration for one species and the metabarcoding data provides information about the relative abundance for tens of species, including hake. Here, we follow and extend the metabarcoding model developed by Shelton et al. (2023) and show how it links with the qPCR model above.

As above, we let $D_s(x,y,d)$ be the log-scale eDNA concentration but now for species $s$. We let $E_{si}(x,y,d)$ be the log-DNA concentration for each species in each bottle. Importantly one of the $s$ species is Pacific hake and so connects to the qPCR model above. Metabarcoding reads are compositional and so we model the DNA concentration relative to one another using the additive log-ratio transformation (ALR; \textbf{Aitchison 1986}).  We define a reference species in each sample, $R$, with the species used as a reference varying among sample. Let $\alpha_s$ be the per PCR cycle log amplification rate for species $s$ (see \cite{shelton2023}).  We can then calculate $\nu_{si}$, the log-ratio between species $s$ and the reference species after accounting for amplification bias (see *Mock Communities* below),

@@

\begin{align} 
 \nu_{sm} &= \left( L_{sm} - L_{Rm}\right) + N_{PCR} \left(\alpha_s - \alpha_{Ri} \right) 
  \pi_{sm} &= \dfrac{e^{\nu_{sm}}}{\sum_{s=1}^S e^{\nu_{sm}}} \\
  \boldsymbol{R}_{m} & \sim Multinomial\left(\boldsymbol{\pi}_{m},T_{m}\right) 
\end{align}

@@

\subsection*{Model convergance}

Gelman-Rubin statistics.  Predicted-observed, etc.

@@

%%% Each figure should be on its own page
\begin{figure}
\centering
\includegraphics[width=0.89\textwidth]{plots/4_Figure_4.jpg}
\caption{Vertical (A) and latitudinal (B) distribution of eDNA concentrations grouped in ecological groups (surface south, surface north, midwater, and deepwater). Mean eDNA concentration of vertical distribution is shown with dots and 99\% upper quantile with ticks (A). Probability density functions (PDF) of estimated eDNA concentrations across latitudinal gradients (B; square root transformed of x-axis to enhance low concentration peaks). Key geographic features, such as the Columbia River and Heceta Bank, are marked to indicate alignment of species distributions.}
\end{figure}

@@

%%% Each figure should be on its own page
\begin{figure}
\centering
\includegraphics[width=0.98\textwidth]{plots/9_Supplementary_Figure_5.jpg}
\caption{Mean posterior predictions for three model compartments, qPCR continuous model (A), qPCR occupancy model (B), mock community model (C and D on species proportions and number of reads) and metabarcoding model (E)}
\end{figure}

@@

\clearpage
\begin{table}\centering
\caption{Initial proportional abundances (measured by amplifying the 12S rRNA gene using MarVer1 primers \cite{valsecchi2020} and ddPCR QX200 Droplet Digital PCR system (Bio-Rad, Inc.)) of the selected species (n=12) across different mock communities (n=8). NA represent no DNA template included.}
    \begin{tabular}{lcccccccc}
        \toprule
        {Species} & \multicolumn{2}{c}{Mock1} & \multicolumn{2}{c}{Mock2} & \multicolumn{2}{c}{Mock3} & \multicolumn{2}{c}{Mock4} \\
        & Even & Skew & Even & Skew & Even & Skew & Even & Skew \\
        \midrule
        \textit{Clupea pallasii}           & 0.437 & 0.325  & 0.042  & 0.009     & -         & -          & 0.025      & 0.038 \\
        \textit{Engraulis mordax}          & 0.122 & 0.034  & 0.15 & 0.15       & 0.146      & 0.16       & 0.308      & 0.478 \\
        \textit{Leuroglossus stilbius}     & 0.108 & 0.29   & - & -         & -         & -         & -         & - \\    
        \textit{Merluccius productus}      & 0.079 & 0.144  & 0.12 & 0.06       & 0.117      & 0.075      & 0.247      & 0.287 \\
        \textit{Microstomus pacificus}     & -    & -     & 0.057  & 0.215     & -         & -         & -         & - \\    
        \textit{Sardinops sagax}           & 0.028 & 0.033  & 0.14 & 0.035      & 0.137      & 0.025      & 0.289      & 0.131 \\
        \textit{Scomber japonicus}         & -    & -     & 0.122  & 0.053      & 0.119      & 0.027     & -         & - \\    
        \textit{Sebastes entomelas}        & -    & -     & - & -          & 0.068      & 0.218     & -         & - \\    
        \textit{Stenobrachius leucopsarus} & -    & -     & - & -          & 0.356      & 0.487     & -         & - \\    
        \textit{Tactostoma macropus}       & -    & -     & 0.13 & 0.324     & -         & -         & -         & - \\    
        \textit{Tarletonbeania crenularis} & -    & -     & 0.083  & 0.124     & -         & -         & -         & - \\    
        \textit{Thaleichthys pacificus}    & 0.123 & 0.113  & 0.099  & 0.012     & -         & -          & 0.013      & 0.021 \\
        \textit{Trachurus symmetricus}     & 0.103 & 0.06   & 0.057  & 0.018      & 0.056      & 0.008      & 0.118      & 0.04 \\
        \bottomrule
    \end{tabular}
\end{table}
\clearpage
\bibliography{Bib.bib}
\end{document}
